

%%%CONTEMPORARY%%%
\documentclass[unnumsec,webpdf,contemporary,large]{oup-authoring-template}%


% line numbers
%\usepackage[mathlines, switch]{lineno}
%\usepackage[right]{lineno}

\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.
\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%
\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}

\begin{document}

\journaltitle{Journal Title Here}
\DOI{DOI HERE}
\copyrightyear{2022}
\pubyear{2019}
\access{Advance Access Publication Date: Day Month Year}
\appnotes{Paper}

\firstpage{1}

%\subtitle{Subject Section}

\title[Short Article Title]{Article Title}

\author[1]{Nathalie Bonin}
\author[1]{Annie Dai}
\author[1]{Emma Shroyer}

\authormark{Author Name et al.}

\address[1]{\orgdiv{Computer Science Department}, \orgname{University of Maryland}, \orgaddress{\state{Maryland}, \country{USA}}}

\corresp[$\ast$]{Corresponding author. \href{email:email-id.com}{email-id.com}}




\abstract{Salmon provides a fast and accurate way to estimate transcript abundance. 
This method uses a dual-phase inference algorithm and takes into account fragment biases for transcript verification. 
However, there are some areas where Salmon could improve. \cite{Pascal_et_al._2023}
The inference algorithms it uses, EM and VBEM, are only point estimates and cannot be checked if there is no ground truth available. 
Further, the choice of prior when using the VBEM algorithm can affect the accuracy of the results. In this work, we test how averaging the inference model predictions affect the accuracy of the inference estimation during Salmon’s offline phase.}
\keywords{Salmon, Tuna, Onefish, Twofish, Redfish, Bluefish}


\maketitle
\input{background.tex}
\input{datasets.tex}
\input{methods.tex}
\input{experiments.tex}
\input{results.tex}
\input{evaluation.tex}
\input{discussion.tex}



\section{Author contributions statement}

Must include all authors, identified by initials, for example:
S.R. and D.A. conceived the experiment(s),  S.R. conducted the experiment(s), S.R. and D.A. analysed the results.  S.R. and D.A. wrote and reviewed the manuscript.

\section{Acknowledgments}
The authors thank the anonymous reviewers for their valuable suggestions. This work is supported in part by funds from the National Science Foundation (NSF: \# 1636933 and \# 1920920).


\bibliographystyle{plain}
\bibliography{reference}


\end{document}
