\section{Future Work}
In our results we saw that using the average of both VBEM and EM is very similar to EM 
when used with a lower prior and more similar to the VBEM output when used with a higher prior. 
We have hypothesized this is because we were taking the average even when one of the results was a 
zero. In future work, we would like to prioritize zero abundances over non-zero abundances. 
Instead of taking the average between value and zero, we want to record the value as zero. 
If neither result is a zero, we wish to take the average of those values. 
We believe this could improve our estimates. 

In the current timeframe, we were unable to expand on our project, but in future work, 
we would like to expand upon ways to best combine the results of the EM and VBEM algorithms. 
Currently, our code is only taking the mean of the two results. 
However, we would also like to experiment with the weighted average or the Bayesian model average 
of these two algorithms also taking into account various prior sizes. 
We hypothesize that this would further improve Salmon’s results \cite{patro_salmon_2017}. 
Additionally, we also would like to test our approach on real life data. 
Although we picked out a dataset consisting of sequencing reads from NK cells, T cells, 
and tumor collected from matched soft tissue sarcoma and peripheral blood \cite{judge_transcriptome_2022}, we were pressed 
for time and resources, and therefore we had to abandon this portion of our project.

We would also like to verify the time it takes to run our combined approach. 
It would be beneficial to run multiple trials to gain an idea of the time it takes to run 
Salmon using our solution. We would like to verify that running this approach will not greatly 
impact the runtime of Salmon. The runtime is expected to increase, since we are running both the 
EM and VBEM algorithms. However, we would like to verify that it is not detrimental to the use 
of Salmon. 

In future work, it would be useful to measure the uncertainty of our trials. 
We were unable to run this during our initial experiments. However, we would like to know if there 
is a level of uncertainty with our results when we use the average of the EM and VBEM algorithms. 
We would like to know if this uncertainty increases or decreases, and if so, whether the change in 
uncertainty is significant. Salmon already supports this analysis through the use of a flag. 
