\section{Results}
We encountered different results depending on the prior selected. Overall, we can separate the outcome of combining both inference algorithms into two categories. The first of such categories includes runs with a prior between $10^{-5}$ and $10^1$, inclusive. As shown in figures \ref{speartable} and \ref{mardtable}, both the $\mathrm{MARD}$ values and the Spearman correlation values are lower for estimates inferred from VBEM than for estimates inferred from both methods (Mann-Whitney U test, $P\leq 1.436 \cdot  10^{-7}$ for MARD, $P < 6.202\cdot 10^{-14}$ for Spearman). However, MARD values tended to be similar between estimates inferred from EM and estimates inferred from both methods (Mann-Whitney U test, $P\geq 0.4803$), whereas the Spearman correlation values were slightly higher for EM (Mann-Whitney U test, $P\leq 0.03941$). Because the MARD metrics are negatively impacted by false discovery rates \cite{patro_salmon_2017}, we hypothesize that the results gathered from running both inference algorithms is affected by EM’s tendency to collect more non-zero abundances than VBEM at low prior values. 

This can also be concluded from the analysis of our second category, which includes runs with a prior of 1 or 10. Unlike with the first category, the $\mathrm{MARD}$ and the Spearman correlation values are strikingly lower for the estimates inferred from EM (Mann-Whitney U test, $P < 6.202\cdot 10^{-14}$ for $\mathrm{MARD}$, $P < 6.202\cdot 10^{-14}$ for Spearman), whereas the difference in MARD between VBEM and the combination of both methods was insignificant for runs with a prior of 1 (Mann-Whitney U test, $P = 0.8944$). The difference between the Spearman correlation values and between the MARD values for runs with a prior of 10 was still significant (Mann-Whitney U test, $P = 5.675 \cdot 10^{-11}$ for $\mathrm{MARD}$, $P < 6.202\cdot 10^{-14}$ for Spearman). We predict that this would suggest that for high prior values, the negative impact from false discovery rates by the VBEM algorithm is offsetted by the more accurate abundance estimates from the EM algorithm. 
\begin{table*}[t]
    \caption{Spearman correlation table for first four samples and their subsamples.
    \label{speartable}}
    \tabcolsep=0pt%%
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
    \toprule
    \begin{tabular}{lrrrrrrrr}
        \textbf{} &
          \multicolumn{1}{l}{Sample $1_{01}$} &
          \multicolumn{1}{l}{Sample $1_{02}$} &
          \multicolumn{1}{l}{Sample $2_{01}$} &
          \multicolumn{1}{l}{Sample $2_{02}$} &
          \multicolumn{1}{l}{Sample $3_{01}$} &
          \multicolumn{1}{l}{Sample $3_{02}$} &
          \multicolumn{1}{l}{Sample $4_{01}$} &
          \multicolumn{1}{l}{Sample $4_{02}$} \\
        EM           & 0.932 & 0.932 & 0.933 & 0.932 & 0.937 & 0.936 & 0.934 & 0.933 \\
        both - $10^{-5}$ & 0.933 & 0.933 & 0.934 & 0.933 & 0.939 & 0.938 & 0.935 & 0.934 \\
        VBEM - $10^{-5}$ & 0.952 & 0.951 & 0.953 & 0.951 & 0.957 & 0.956 & 0.954 & 0.952 \\
        both - $10^{-4}$ & 0.933 & 0.933 & 0.934 & 0.933 & 0.939 & 0.938 & 0.935 & 0.934 \\
        VBEM - $10^{-4}$ & 0.952 & 0.951 & 0.953 & 0.951 & 0.957 & 0.956 & 0.954 & 0.952 \\
        both - $10^{-3}$ & 0.933 & 0.933 & 0.934 & 0.933 & 0.939 & 0.938 & 0.935 & 0.934 \\
        VBEM - $10^{-3}$ & 0.952 & 0.951 & 0.953 & 0.951 & 0.957 & 0.956 & 0.954 & 0.952 \\
        both - $10^{-2}$ & 0.933 & 0.933 & 0.934 & 0.933 & 0.939 & 0.938 & 0.935 & 0.934 \\
        VBEM - $10^{-2}$ & 0.952 & 0.951 & 0.953 & 0.952 & 0.957 & 0.956 & 0.954 & 0.952 \\
        both - $10^{-1}$ & 0.933 & 0.933 & 0.934 & 0.933 & 0.939 & 0.937 & 0.935 & 0.934 \\
        VBEM - $10^{-1}$ & 0.951 & 0.950 & 0.953 & 0.951 & 0.957 & 0.955 & 0.954 & 0.951 \\
        both - $10^{0}$  & 0.755 & 0.754 & 0.755 & 0.754 & 0.755 & 0.755 & 0.755 & 0.754 \\
        VBEM - $10^{0}$  & 0.751 & 0.751 & 0.751 & 0.751 & 0.752 & 0.752 & 0.751 & 0.751 \\
        both - $10^{1}$  & 0.736 & 0.735 & 0.736 & 0.736 & 0.738 & 0.737 & 0.736 & 0.736 \\
        VBEM - $10^{1}$  & 0.715 & 0.715 & 0.715 & 0.716 & 0.717 & 0.717 & 0.715 & 0.715 \\
        \botrule    
    \end{tabular}
    
    \end{tabular*}
    \end{table*}